Figure 2 and figure 2 supplementary material

### 2022-03-10 Figures/Figure2.Rmd
add Figure2 corrplot average row

    order <- store_corrs %>% group_by(measure2) %>% dplyr::summarize(meanr = mean(r)) %>% arrange(desc(meanr))
    ct_corrplots[[ct]] <- dplyr::mutate(store_corrs, measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange( factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}

>>>>

    order <- store_corrs %>% 
      group_by(measure2) %>%
      dplyr::summarize(r = mean(r)) %>% 
      arrange(desc(r)) %>% 
      mutate(measure1 = "Average",
             p = NA,
             sig_p = TRUE,
             p_if_sig = NA,
             r_if_sig = r ) %>%
      dplyr::relocate(measure1, .before = measure2)

    ct_corrplots[[ct]] <- add_row(store_corrs, order) %>% dplyr::mutate(measure2 = factor(measure2, levels = order$measure2)) %>% dplyr::arrange(factor(measure2, levels = order$measure2)) %>%
    ggplot(aes(measure2, measure1, fill=r, label=round(r_if_sig,2))) +
    geom_tile() +
      labs(x = NULL, y = NULL, fill = "Spearman's\nCorrelation", title= ct, 
         subtitle="Only significant correlation coefficients shown (95% I.C.)") +
    scale_fill_gradient2(mid="#FBFEF9",low="#0C6291",high="#A63446", limits=c(-1,1)) +
    geom_text() +
    theme_classic() +
    scale_x_discrete(expand=c(0,0)) +
    scale_y_discrete(expand=c(0,0)) +
    rotate_x_text(angle = 45)
   }
  return(ct_corrplots)
}
